Independent Contractor Agreement

### 2015-12-14 contract/contact.tex
added linear algebra submodule

@@

>>>>

The application will undergo testing before release and during times when the application is being upgraded, and will be compleated in a timely fashion as agreed upon by the developer and the contractor.

@@

In addition, the developer must be allowed to claim credit for the devlopment of the application both before and after the application is released.
